Structured Versus Decorated Cospans

### 2021-03-22 cospans_new.tex
added Shulman's name for "Beck-Chevalley"
added stuff about new proofs

We prove both these theorems using the work of Shulman \cite{Shulman2008}, which we recall here.   First we need a few concepts.   Opfibrations are recalled in \cref{subsec:fibrations}, 
and fibrations are defined dually, with a functor $\Phi \maps \C \to \A$ being a fibration if and only
if $\Phi\op \maps \C\op \to \A\op$ is an opfibration.   A functor $\Phi \maps \C \to \A$ is a \define{bifibration} if it is both a fibration and an opfibration.  If $\Phi \maps \C \to \A$ an opfibration we have for any morphism $f \maps a \to b$ in $\A$ a covariant reindexing functor
\[    f_! \maps \C_a \to \C_b \]
between the fibers of $\Phi$, as recalled in \cref{subsec:fibrations}.  Similarly, if $\Phi$ is a fibration we have a contravariant reindexing functor
\[    f^\ast \maps \C_b \to \C_a .\]
Thus, in a bifibration we have both covariant and contravariant reindexing functors, and in 
fact $f^\ast$ is left adjoint to $f_\ast$ \cite[Proposition 3.9]{Shulman2008}.   Using this one can easily show that for any commutative square in $\A$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$b$};
\node (C) at (0,-1) {$c$};
\node (D) at (1,-1) {$d$};
%\node (E) at (0.5,-0.5) {$\Downarrow\theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$g$} (D)
(C) edge node[below]{$f$} (D);
\end{tikzpicture}
\]
the following square commutes up to a natural transformation:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\C_a$};
\node (B) at (1,0) {$\C_b$};
\node (C) at (0,-1) {$\C_c$};
\node (D) at (1,-1) {$\C_d$};
\node (E) at (0.5,-0.5) {$\Searrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(B) edge node[above]{$h^\ast$} (A)
(A) edge node[left]{$k_!$} (C)
(B) edge node[right]{$g_!$} (D)
(D) edge node[below]{$f^\ast$} (C);
\end{tikzpicture}
\]
If $\theta$ is a natural isomorphism whenever the original square in $\A$ was
a pushout, we say $\Phi$ is \define{Beck--Chevalley}.

@@

\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] We apply \cref{lem:shulman} to ....
\end{proof}

\begin{proof}[Proof of \cref{thm:decorated_cospans_2}] We apply \cref{lem:shulman} to ....
\end{proof}

@@

{\bf NEW PROOF HERE.}  We apply \cref{lem:shulman} to ....
\end{proof}

>>>>

We prove both these theorems using the work of Shulman \cite{Shulman2008}, which we recall here.   First we need a few concepts.   Opfibrations are recalled in \cref{subsec:fibrations}, 
and fibrations are defined dually, with a functor $\Phi \maps \C \to \A$ being a fibration if and only
if $\Phi\op \maps \C\op \to \A\op$ is an opfibration.   A functor $\Phi \maps \C \to \A$ is a \define{bifibration} if it is both a fibration and an opfibration.  If $\Phi \maps \C \to \A$ an opfibration we have for any morphism $f \maps a \to b$ in $\A$ a covariant reindexing functor
\[    f_! \maps \C_a \to \C_b \]
between the fibers of $\Phi$, as recalled in \cref{subsec:fibrations}.  Similarly, if $\Phi$ is a fibration we have a contravariant reindexing functor
\[    f^\ast \maps \C_b \to \C_a .\]
Thus, in a bifibration we have both covariant and contravariant reindexing functors, and in 
fact $f^\ast$ is left adjoint to $f_\ast$ \cite[Proposition 3.9]{Shulman2008}.   Using this one can easily show that for any commutative square in $\A$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$b$};
\node (C) at (0,-1) {$c$};
\node (D) at (1,-1) {$d$};
%\node (E) at (0.5,-0.5) {$\Downarrow\theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$g$} (D)
(C) edge node[below]{$f$} (D);
\end{tikzpicture}
\]
the following square commutes up to a natural transformation:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\C_a$};
\node (B) at (1,0) {$\C_b$};
\node (C) at (0,-1) {$\C_c$};
\node (D) at (1,-1) {$\C_d$};
\node (E) at (0.5,-0.5) {$\Searrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(B) edge node[above]{$h^\ast$} (A)
(A) edge node[left]{$k_!$} (C)
(B) edge node[right]{$g_!$} (D)
(D) edge node[below]{$f^\ast$} (C);
\end{tikzpicture}
\]
If $\theta$ is a natural isomorphism whenever the original square in $\A$ was
a pushout, we say $\Phi$ is \define{Beck--Chevalley}.  (Shulman says `strongly co-Beck--Chevalley'.)

@@

\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] We apply \cref{lem:shulman} to $A/U \to A$: why is this a fibration, a cofibration, and Beck--Chevalley?
\end{proof}

\begin{proof}[Proof of \cref{thm:decorated_cospans_2}] We apply \cref{lem:shulman} to $A/U \to A$: why is this a symmetric monoidal bifibration?
\end{proof}

@@

{\bf NEW PROOF HERE.}  We apply \cref{lem:shulman} to $L/X \to A$.   Why is this a fibration, cofibration, Beck--Chevalley and symmetric monoidal?
\end{proof}
